ZCB Pricing

### 2018-08-07 Draft.tex
abstract

\begin{abstract}
	Something interesting in this section
\end{abstract}

>>>>

\begin{abstract}
	This paper examines the methods used to price a zero coupon bonds under the Ornstein Uhenbleck process. This paper considers the use Monte Carlo simulations together with various variance reduction techniques to verify improvments in stability of estimates. The simulation method is compared to various finitie difference techniques to analyse the difference in convergence and speed in evaluating solutions.The various methods are compared to the closed form solution to assess the accuracy. 
\end{abstract}
